\documentclass{hwByKicker}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amssymb}

\hwName{Name}
\hwClass{Class}
\hwAssignment{Assignment}
\hwDate{February 27, 2015}

% Paragraph formatting
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\hwskip{-0.5em}

\begin{document}

\hwgroupheading{Questions about questions}
\hwquestion{What is a question?}
A question is something that needs an answer. 

\hwquestion{Why do some questions have multiple parts?}
\hwsubquestion{Should related questions be relegated to 
subquestions?}
Not unless they help to answer one larger question. 

\hwsubquestion{What is the purpose of breaking questions down?}
Some questions have multiple steps that need answering one 
by one. 
It is sometimes easier to break them down into subquestions.

\hwsubsubquestion{Why do some sub questions have multiple parts?}
Subquestions ask about algorithms or something else that 
requires multiple steps. 

\hwsubsubquestion{What is the purpose of breaking sub questions down?}
To make each step more clear. 

\hwsubsubquestion{Should you break down something that really only has one part?}
No. That would be silly.

\hwresetmargin
Here is a paragraph of text in-between questions. 
Why would this be necessary? 
I really am not sure, but there is probably a use for it. 

\hwgroupheading{MARVEL}
\hwquestion{What is S.H.I.E.L.D.?}
An organization that protects the world from technology it 
is not ready for. 
This can include alien technology. 

\hwquestion{What does S.H.I.E.L.D. stand for?}
\hwsubquestion{What was its original meanig?}
Supreme Headquarters, Internationl Espionage, Law-Enforcement 
Division

\hwsubquestion{What is its currend meaning?}
Strategic Homeland Intervention Espionage Logistics Directorate 

\hwquestion{Who is the current director of S.H.I.E.L.D.?}
Phil Coulson ... However, Nick Fury is still involved. 

\hwresetmargin
This is another random paragraph just to show it can be done

\end{document}
